### 2015-02-12 paper_40_mpi.tex
finished availability

@@

                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.

@@

            \paragraph{AVAILABILITY FORMULA}
            \begin{displaymath}
               S_{3_i} = \left\{
                 \begin{array}{lr}
                   \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
                   \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
                 \end{array}
               \right.
            \end{displaymath} 
            \[
                S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
            \]

            \begin{itemize}
            \item $A_{a_i}$ actual availability for app i
            \item $A_{e_i}$ expected availability for app i
            \end{itemize}

>>>>

                Then the overall quality score is calculated as below.

@@

                The preferred method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.  Thus, the Percent Uptime is important
                and it can either be supplied in the data or calculated from the 
                optional fields.

@@

            \paragraph{AVAILABILITY FORMULA}
                The formula for availability is more straightforward than the quality formula.
                It does not include any analysis of the historic data.  That lack of historical
                analysis is avoided since the SLA provides an existing baseline to measure 
                against.  The following formula is simply a percentage the SLA was exceeded
                or missed.

                \begin{displaymath}
                   S_{2_i} = \left\{
                     \begin{array}{lr}
                       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\times k \right] \\
                       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\times k \right]
                     \end{array}
                   \right. \text{   , calculate availability score for each app $i$}
                \end{displaymath}

                where

                \begin{itemize}
                    \item $A_{a_i}$ actual availability for System ID $i$
                    \item $A_{e_i}$ expected availability for System ID $i$
                \end{itemize}

                Then the overall availability score is calculated as below.

                \[
                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                \]
